Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-10-08 write_up/Supplementary.tex
Text updates to JJP

\title{MixFishSim: Supplementary Figures and Tables}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/habitat}
	\caption{habitat preference}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
	\caption{spawning habitat preference}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Temperature_gradient}
	\caption{Spatiotemporal temperature gradient}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Species_tolerances}
	\caption{Species thermal tolerances}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
	\caption{Spatiotemporal habitat suitability - population 1}
	\label{fig:5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
	\caption{Spatiotemporal habitat suitability - population 2}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_3}
	\caption{Spatiotemporal habitat suitability - population 3}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
	\caption{Spatiotemporal habitat suitability - population 4}
	\label{fig:8}
\end{figure}

>>>>

\title{MixFishSim: Supplementary Figures}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/habitat}
	\caption{Habitat preference: the distribution of suitable habitat for
		each population, with the darker colour showing greater
		suitability.}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/habitat_spwn}
	\caption{Spawning habitat preference: the habitat suitability during
		spawning periods for each population.}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Temperature_gradient}
	\caption{Spatiotemporal temperature gradient: The temperature gradient
	for each time step (weeks, shown in top right corner of each panel.)}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Species_tolerances}
	\caption{Species thermal tolerances: The tolerance of each population
		to different temperatures (x-axis) shown as a probability
		density function.}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_1}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 1) for 52 separate weeks.}
	\label{fig:5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_2}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 2) for 52 separate weeks.}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_3}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 3) for 52 separate weeks}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 4) for 52 separate weeks}
	\label{fig:8}
\end{figure}

### 2019-10-08 write_up/mixfishsim_ecolmod.tex
Update figure
Text updates to JJP

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c
\in \mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the
joint distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian
with a \textit{Matérn} covariance structure, where the correlation strength
weakens with distance controlled by two parameters, with $\nu$ a scale
parameter in the units of distance and $\kappa$ a shape parameter which
determines the smoothness of the process. This enables us to model the spatial
autocorrelation observed in animal populations where density is more similar in
nearby locations \citep{Tobler1970, F.Dormann2007, Poos2007} and we change the
parameters to implement different spatial structures for the different
populations using the \textit{RandomFields} R package \citep{Schlater2015}. We
define a stationary habitat field with an anisotropic pattern (to simulate a
depth gradient) and combine it with a temporally dynamic thermal tolerance
field to imitate two key drivers of population dynamics without modelling the
processes explicitly. Each population was initialised at a single location, and
subsequently moved across the entire space according to a probabilistic
distribution based on habitat suitability (represented by the normalised values
from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{I,J}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{c,p}^2$ is the squared index of
habitat suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
temperature tolerance for cell $c$ by population $p$ in week $wk$ (see
below). \\

@@

A time-varying temperature covariate changes the interaction between time and
suitable habitat on a weekly time-step. Each population $p$ was assigned a
thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma^2_{p}$ the mean and standard deviation of the population
temperature tolerance. \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
	\caption{Effectiveness of closure with regards to reducing fishing
		mortality on protected population (further left on x-axis is
		best) and maintaining high catches in the fishery (highest on
		y-axis is best). The grey line indicates the direction of the
		trade-off between reducing fishing mortality and overall
		catches.}
	\label{fig:ce}
\end{figure}

>>>>

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c
\in \mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the
joint distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian
with a \textit{Matérn} covariance structure, where the correlation strength
weakens with distance controlled by two parameters, with $\nu$ a scale
parameter in the units of distance and $\kappa$ a shape parameter which
determines the smoothness of the process. This enables us to model the spatial
autocorrelation observed in animal populations where density is more similar in
nearby locations \citep{Tobler1970, F.Dormann2007, Poos2007} and we change the
parameters to implement different spatial structures for the different
populations using the \textit{RandomFields} R package \citep{Schlater2015}. We
define a stationary habitat field with an anisotropic pattern (to simulate a
depth gradient) and combine it with a temporally dynamic thermal tolerance
field to imitate two key drivers of population dynamics without modelling the
processes explicitly. Each population was initialised at a single location, and
subsequently moved across the entire space according to a probabilistic
distribution based on habitat suitability (represented by the normalised values
from the GRFs), temperature tolerance and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{I,J}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{c,p}$ is the index of habitat
suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
temperature tolerance for cell $c$ by population $p$ in week $wk$ (see below).
\\

@@

A time-varying temperature covariate changes the interaction between time and
suitable habitat on a weekly time-step. Each population $p$ was assigned a
thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so that
each cell and population temperature tolerance is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma_{p}$ the mean and standard deviation of the population temperature
tolerance. \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
	\caption{Effectiveness of closure with regards to reducing fishing
		mortality on protected population (further left on x-axis is
		best) and maintaining high catches in the fishery (highest on
		y-axis is best). The numbers indicate the spatial resolution of
		the data, while grey lines indicate the direction of the
		trade-off between reducing fishing mortality and overall
		catches.}
	\label{fig:ce}
\end{figure}

### 2019-10-08 write_up/parameter_tables.tex
Small update to Table 4
Text updates to JJP

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module.}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell $c$ in week $wk$ & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population $p$ & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		population $p$ & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & Decay rate for population movement & - \\
		$Hab_{c,p}$ & Habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
		for population $p$ & - \\
		$d_{I,J}$ & Euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

@@

\begin{table}[!ht]
\caption{Population dynamics and movement parameter settings.}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier = 10 & & & & \\
	Movement $\lambda$ = 0.1 & & & & \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit $\alpha$ & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit $\beta$ & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ = 0.3 & & & & \\
	$wt$ = 1 & & & & \\
	$wt_{d-1}$ = 0.1 & & & &  \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu$ & 12 & 15 & 17 & 14 \\
	$\sigma^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

>>>>

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module.}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell $c$ in week $wk$ & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population $p$ & $^\circ$C \\
		$\sigma_{p}$ & Standard deviation of thermal tolerance for
		population $p$ & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & Decay rate for population movement & - \\
		$Hab_{c,p}$ & Habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
		for population $p$ & - \\
		$d_{I,J}$ & Euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

@@

\begin{table}[!ht]
\caption{Population dynamics and movement parameter settings.}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier = 10 & & & & \\
	Movement $\lambda$ = 0.1 & & & & \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit $\alpha$ & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit $\beta$ & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ = 0.3 & & & & \\
	$wt$ = 1 & & & & \\
	$wt_{d-1}$ = 0.1 & & & &  \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu_{p}$ & 12 & 15 & 17 & 14 \\
	$\sigma_{p}^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}
